Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-13 aistats.tex
Clean the end of Open Problem

\paragraph{Optimization}
We can rewrite~\eqref{eq:defMAP} as
\alignn{
\m_n = \m_{n-1}- \lr_n (\m_{n-1} - T_n)
\label{eq:mean_update}
}
where $\lr_n := \inv{n_0 + n}$. 
Now let $f_X(\nat) = -\log p(X \cond \nat)$ such that $\E[f_X] = f$.
If we further introduce $g_n(\nat) := \nabla\logpart(\nat) - T_n = \nabla f_{X_n}(\nat)$, then~\eqref{eq:mean_update} becomes
\alignn{
\nabla\conj(\hat \nat_{n}) 
= \nabla\conj(\hat \nat_{n-1}) - \lr_n g_n(\hat \nat_{n-1})
}
which we recognize as the update formula for stochastic mirror descent (SMD) on $f$ with mirror map $\nabla\logpart$ and step-size schedule $\lr_n$.

@@

Surprisingly, we found no general solution to this seemingly simple problem, whether in the literature or by our own means.
%TODO. what we did and are going to present next.
We are yet to find a solution encompassing a broad range of exponential families, and applicable to small sample sizes $n$.

{\bf Remark.}
While~\eqref{eq:bregmanMAP} is always finite, \eqref{eq:bregmanMLE} may be infinite, 
for instance in Gaussian covariance estimation when $n \leq d + 1$.
Even worse with categorical variables, the MLE is always ill-defined. %TODO
Instead of taking the expectation, one might want to bound the risk in high probability, without resorting to Markov inequality.

\section{Insights}

@@

\section{Examples}

>>>>

\paragraph{Optimization}
We can rewrite~\eqref{eq:defMAP} as
\alignn{
\m_n = \m_{n-1}- \lr_n (\m_{n-1} - T_n)
\label{eq:mean_update}
}
where $\lr_n := \inv{n_0 + n}$. 
Now let $f_X(\nat) = -\log p(X \cond \nat)$ such that $\E[f_X] = f$.
If we further introduce $g_n(\nat) := \nabla\logpart(\nat) - T_n = \nabla f_{X_n}(\nat)$, then~\eqref{eq:mean_update} becomes
\alignn{
\nabla\conj(\hat \nat_{n}) 
= \nabla\conj(\hat \nat_{n-1}) - \lr_n g_n(\hat \nat_{n-1})
}
which we recognize as the update formula for stochastic mirror descent (SMD) on $f$ with mirror map $\nabla\logpart$ and step-size schedule $\lr_n$.
\emph{MAP is an instantiation of SMD.}

@@

Surprisingly, we found no general solution to this seemingly simple problem, whether in the literature or by our own means.
There is a large body of work about asymptotic or large sample results, which we partially review in \S\ref{sec:insights}.
There are also results for special cases, such as $\cN(0, \sigma^2)$ (See \S\ref{sec:example}). 
But we are yet to find a solution encompassing a broad range of exponential families, and applicable to small sample sizes $n \lesssim d$.

{\bf Unboundedness of~\eqref{eq:bregmanMLE}.}
While~\eqref{eq:bregmanMAP} is always finite, \eqref{eq:bregmanMLE} may be infinite, 
for instance in Gaussian covariance estimation when $n \leq d + 1$.
Even worse, with categorical variables, there is always a non-zero probability to never sample one of the categories. In such the MLE will give zero weight to this category and $KL(p_{\nat^*} || p_\text{MLE} ) = +\infty$. 
This means that the expected KL~\eqref{eq:bregmanMLE} is infinite for any number of samples.
Instead of taking the expectation, one might want to bound the risk in high probability, without resorting to Markov inequality but this is a difficult endeavor.
These examples are rather making a case for regularized estimators such as MAP, for which we may find interesting upper bounds.

\section{Insights}
\label{sec:insights}

@@

\section{Examples}
\label{sec:example}
